Decentralized Active Damping of Rotating Positioning Platforms

### 2020-06-25 paper/paper.tex
Start to rewrite all the equations

% Created 2020-06-24 mer. 16:28
% Intended LaTeX compiler: pdflatex
\documentclass{ISMA_USD2020}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage{subcaption}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author[1,3] {T. Dehaeze}
\author[1,2] {C. Collette}
\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
\bibliographystyle{IEEEtran}
\usepackage{tikz}
\usetikzlibrary{shapes.misc}
\date{}
\title{Active Damping of Rotating Positioning Platforms}
\begin{document}

@@

\section{Introduction}
\label{sec:org3cbd2ff}
\label{sec:introduction}
Controller Poles are shown by black crosses (
\begin{tikzpicture} \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){}; \end{tikzpicture}
).
This paper has been published
The Matlab code that was use to obtain the results are available in \cite{dehaeze20_activ_dampin_rotat_posit_platf}.

\section{Dynamics of Rotating Positioning Platforms}
\label{sec:org3cf58d1}
\subsection{Studied Rotating Positioning Platform}
\label{sec:orgf321431}
Consider the rotating X-Y stage of Figure \ref{fig:system}.

@@

\subsection{Equation of Motion}
\label{sec:org9612ace}
The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\) (describing the position of the mass in the rotating frame).

Let's express the kinetic energy \(T\) and the potential energy \(V\) of the mass \(m\) (neglecting the rotational energy):

Dissipation function \(R\)
Kinetic energy \(T\)
Potential energy \(V\)
\begin{subequations}
  \begin{align}
    T & = \frac{1}{2} m \left( \left( \dot{u} - \Omega v \right)^2 + \left( \dot{v} + \Omega u \right)^2 \right) \\
    R & = \frac{1}{2} c \left( \dot{u}^2 + \dot{v}^2 \right) \\
    V & = \frac{1}{2} k \left( u^2 + v^2 \right)
  \end{align}
\end{subequations}

The Lagrangian is the kinetic energy minus the potential energy:
\begin{equation}
L = T - V
\end{equation}

From the Lagrange's equations of the second kind, the equation of motion is obtained (\(q_1 = u\), \(q_2 = v\)).
\begin{equation}
  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
\end{equation}
with \(Q_i\) is the generalized force associated with the generalized variable \(q_i\) (\(Q_1 = F_u\) and \(Q_2 = F_v\)).

\begin{subequations}
  \begin{align}
    m \ddot{u} + c \dot{u} + ( k - m \Omega ) u &= F_u + 2 m \Omega \dot{v} \\
    m \ddot{v} + c \dot{v} + ( k \underbrace{-\,m \Omega}_{\text{Centrif.}} ) v &= F_v \underbrace{-\,2 m \Omega \dot{u}}_{\text{Coriolis}}
  \end{align}
\end{subequations}

\begin{itemize}
\item Coriolis Forces: coupling
\item Centrifugal forces: negative stiffness
\end{itemize}

Without the coupling terms, each equation is the equation of a one degree of freedom mass-spring system with mass \(m\) and stiffness \(k- m\dot{\theta}^2\).
Thus, the term \(- m\dot{\theta}^2\) acts like a negative stiffness (due to \textbf{centrifugal forces}).

\subsection{Transfer Functions in the Laplace domain}
\label{sec:org1590670}

\begin{subequations}
  \begin{align}
    u &= \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_u +  \frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_v \\
    v &= \frac{-2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_u +  \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_v
  \end{align}
\end{subequations}

\begin{equation}
\begin{bmatrix} d_u \\ d_v \end{bmatrix} =
\bm{G}_d
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}
Where \(\bm{G}_d\) is a \(2 \times 2\) transfer function matrix.

@@

\begin{itemize}
\item \(\omega_0 = \sqrt{\frac{k}{m}}\): Natural frequency of the mass-spring system in \(\si{\radian/\s}\)
\item \(\xi\) damping ratio
\end{itemize}

\subsection{Constant Rotational Speed}
\label{sec:orgd9375df}
To simplify, let's consider a constant rotational speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).

\begin{equation}
\label{eq:coupledplant}
\begin{bmatrix} d_u \\ d_v \end{bmatrix} =
\frac{1}{(m s^2 + (k - m{\omega_0}^2))^2 + (2 m {\omega_0} s)^2}
\begin{bmatrix}
  ms^2 + (k-m{\omega_0}^2) & 2 m \omega_0 s \\
  -2 m \omega_0 s          & ms^2 + (k-m{\omega_0}^2) \\
\end{bmatrix}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}

\begin{equation}
\label{eq:coupled_plant}
\begin{bmatrix} d_u \\ d_v \end{bmatrix} =
\frac{\frac{1}{k}}{\left( \frac{s^2}{{\omega_0}^2} + (1 - \frac{{\Omega}^2}{{\omega_0}^2}) \right)^2 + \left( 2 \frac{{\Omega} s}{{\omega_0}^2} \right)^2}
\begin{bmatrix}
  \frac{s^2}{{\omega_0}^2} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} & 2 \frac{\Omega s}{{\omega_0}^2} \\
  -2 \frac{\Omega s}{{\omega_0}^2}          & \frac{s^2}{{\omega_0}^2} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \\
\end{bmatrix}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}

When the rotation speed is null, the coupling terms are equal to zero and the diagonal terms corresponds to one degree of freedom mass spring system.
\begin{equation}
\label{eq:coupled_plant_no_rot}
\begin{bmatrix} d_u \\ d_v \end{bmatrix} =
\frac{\frac{1}{k}}{\frac{s^2}{{\omega_0}^2} + 1}
\begin{bmatrix}
  1 & 0 \\
  0 & 1
\end{bmatrix}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}

When the rotation speed in not null, the resonance frequency is duplicated into two pairs of complex conjugate poles.
As the rotation speed increases, one of the two resonant frequency goes to lower frequencies as the other one goes to higher frequencies (Figure \ref{fig:campbell_diagram}).

@@

The magnitude of the coupling terms are increasing with the rotation speed.

\section{Integral Force Feedback}
\label{sec:org95f47e8}
\subsection{Control Schematic}
\label{sec:org8bb26ea}

@@

\subsection{Equations}
\label{sec:orgbd9ebe0}
The sensed forces are equal to:
\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
\begin{bmatrix} d_u \\ d_v \end{bmatrix}
\end{equation}

Which then gives:
\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\bm{G}_{f}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}

\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\frac{1}{G_{fp}}
\begin{bmatrix}
  G_{fz} & -G_{fc} \\
  G_{fc} &  G_{fz}
\end{bmatrix}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}

@@

\subsection{Plant Dynamics}
\label{sec:org392809f}

@@

\subsection{Integral Force Feedback}
\label{sec:org049877c}

@@

\section{Integral Force Feedback with High Pass Filters}
\label{sec:org54452db}
\subsection{Modification of the Control Low}
\label{sec:org325cdd4}

\subsection{Feedback Analysis}
\label{sec:org5efee77}

@@

\subsection{Optimal Cut-Off Frequency}
\label{sec:orgd5828e4}

@@

\section{Integral Force Feedback with Parallel Springs}
\label{sec:org22884d6}
\subsection{Stiffness in Parallel with the Force Sensor}
\label{sec:orgb871bfd}

@@

\subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
\label{sec:org4d37cce}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_iff_kp.pdf}
\caption{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without any parallel stiffness, with a parallel stiffness \(k_p < m \Omega^2\) and with \(k_p > m \Omega^2\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kp.pdf}
\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without any parallel stiffness, with a parallel stiffness \(k_p < m \Omega^2\) and with \(k_p > m \Omega^2\)}
\end{figure}

\subsection{Optimal Parallel Stiffness}
\label{sec:orgd19b212}

@@

\section{Direct Velocity Feedback}
\label{sec:org6904969}
\subsection{Control Schematic}
\label{sec:org103e18b}

@@

\subsection{Equations}
\label{sec:org793c22d}

\subsection{Relative Direct Velocity Feedback}
\label{sec:orgc28d518}

@@

\section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
\label{sec:org6af1fdb}
\subsection{Physical Comparison}
\label{sec:orgdff3aa2}

\subsection{Attainable Damping}
\label{sec:org22c8f42}

@@

\subsection{Transmissibility and Compliance}
\label{sec:org3e2cf56}

@@

\section{Conclusion}
\label{sec:orge292803}
\label{sec:conclusion}

\section*{Acknowledgment}
\label{sec:orgaf681fb}

>>>>

% Created 2020-06-25 jeu. 10:07
% Intended LaTeX compiler: pdflatex
\documentclass{ISMA_USD2020}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage{subcaption}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author[1,3] {T. Dehaeze}
\author[1,2] {C. Collette}
\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
\bibliographystyle{IEEEtran}
\usepackage{tikz}
\usetikzlibrary{shapes.misc}
\date{}
\title{Decentralized Active Damping of Rotating Positioning Platforms}
\hypersetup{
 pdfauthor={},
 pdftitle={Decentralized Active Damping of Rotating Positioning Platforms},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
 pdflang={English}}
\begin{document}

@@

\section{Introduction}
\label{sec:org5780a8f}
\label{sec:introduction}
Controller Poles are shown by black crosses (
\begin{tikzpicture} \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){}; \end{tikzpicture}
).
This paper has been published
The Matlab code that was use to obtain the results are available in \cite{dehaeze20_activ_dampin_rotat_posit_platf}.

\section{Dynamics of Rotating Positioning Platforms}
\label{sec:orga8db619}
\subsection{Studied Rotating Positioning Platform}
\label{sec:org70ddefe}
Consider the rotating X-Y stage of Figure \ref{fig:system}.

@@

\subsection{Equations of Motion}
\label{sec:org647b64d}
The system has two degrees of freedom and is thus fully described by the generalized coordinates \([q_1\ q_2] = [d_u\ d_v]\) (describing the position of the mass in the rotating frame).

Let's express the kinetic energy \(T\), the potential energy \(V\) of the mass \(m\) (neglecting the rotational energy) as well as the deceptive function \(R\):
\begin{subequations}
\label{eq:energy_functions_lagrange}
  \begin{align}
    T & = \frac{1}{2} m \left( \left( \dot{d}_u - \Omega d_v \right)^2 + \left( \dot{d}_v + \Omega d_u \right)^2 \right) \\
    V & = \frac{1}{2} k \left( {d_u}^2 + {d_v}^2 \right) \\
    R & = \frac{1}{2} c \left( \dot{d}_u{}^2 + \dot{d}_v{}^2 \right)
  \end{align}
\end{subequations}

The equations of motion are derived from the Lagrangian equation:
\begin{equation}
\label{eq:lagrangian_equations}
  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
\end{equation}
with \(L = T - V\) is the Lagrangian and \(Q_i\) is the generalized force associated with the generalized variable \(q_i\) (\(Q_1 = F_u\) and \(Q_2 = F_v\)).

\begin{subequations}
\label{eq:eom_coupled}
  \begin{align}
    m \ddot{d}_u + c \dot{d}_u + ( k - m \Omega ) d_u &= F_u + 2 m \Omega \dot{d}_v \\
    m \ddot{d}_v + c \dot{d}_v + ( k \underbrace{-\,m \Omega}_{\text{Centrif.}} ) d_v &= F_v \underbrace{-\,2 m \Omega \dot{d}_u}_{\text{Coriolis}}
  \end{align}
\end{subequations}

The Gyroscopic effects can be seen from the two following terms:
\begin{itemize}
\item Coriolis Forces: coupling
\item Centrifugal forces: negative stiffness
\end{itemize}

\subsection{Transfer Functions in the Laplace domain}
\label{sec:org55c9228}

Using the Laplace transformation on the equations of motion \eqref{eq:eom_coupled}, the transfer functions from \([F_u,\ F_v]\) to \([d_u,\ d_v]\) are obtained:
\begin{subequations}
\label{eq:oem_laplace_domain}
  \begin{align}
    d_u &= \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_u +  \frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_v \\
    d_v &= \frac{-2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_u +  \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} F_v
  \end{align}
\end{subequations}

Without rotation \(\Omega = 0\) and the system corresponds to two uncoupled one degree of freedom mass-spring-damper systems:
\begin{subequations}
\label{eq:oem_no_rotation}
  \begin{align}
    d_u &= \frac{1}{m s^2 + cs + k} F_u \\
    d_v &= \frac{1}{m s^2 + cs + k} F_v
  \end{align}
\end{subequations}

\subsection{Change of Variables / Parameters for the study}
\label{sec:orgb7d090c}

In order this study is more independent on the system parameters, the following change of variable is performed:
\begin{itemize}
\item \(\omega_0 = \sqrt{\frac{k}{m}}\): Natural frequency of the mass-spring system in \(\si{\radian/\s}\)
\item \(\xi = \frac{c}{2 \sqrt{k m}}\): Damping ratio
\end{itemize}

\begin{equation}
\label{eq:tf_d}
  \begin{bmatrix} d_u \\ d_v \end{bmatrix} = \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}
Where \(\bm{G}_d\) is a \(2 \times 2\) transfer function matrix.

@@

\(G_{dp}\) describes to poles of the system, \(G_{dz}\) the zeros of the diagonal terms and \(G_{dc}\) the coupling.

\subsection{System Dynamics and Campbell Diagram}
\label{sec:org24f5f5f}
The bode plot of \(\bm{G}_d\) is shown in Figure \ref{fig:plant_compare_rotating_speed}.

When the rotation speed in non-null, the resonance frequency is split into two pairs of complex conjugate poles.
As the rotation speed increases, one of the two resonant frequency goes to lower frequencies as the other one goes to higher frequencies.

When the rotational speed \(\Omega\) reaches \(\omega_0\), the real part of one pair of complex conjugate becomes position meaning is system is unstable.

The stiffness of the X-Y stage is too small to hold to rotating payload hence the instability.

Stiff positioning platforms should be used if high rotational speeds or heavy payloads are used.

@@

\section{Decentralized Integral Force Feedback}
\label{sec:orgd957fd6}
\subsection{Control Schematic}
\label{sec:orgc01d8cf}

@@

\subsection{Equations}
\label{sec:orge5896ec}
The forces measured by the force sensors are equal to:
\begin{equation}
\label{eq:measured_force}
  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
  \begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
  \begin{bmatrix} d_u \\ d_v \end{bmatrix}
\end{equation}

Reinjecting \eqref{eq:tf_d} into \eqref{eq:measured_force} yields:
\begin{equation}
\label{eq:tf_f}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} = \bm{G}_{f} \begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}

\begin{equation}
\bm{G}_f =
\frac{1}{G_{fp}}
\begin{bmatrix}
  G_{fz} & -G_{fc} \\
  G_{fc} &  G_{fz}
\end{bmatrix}
\end{equation}

@@

\begin{equation}
\bm{G}_f =
\frac{1}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
\begin{bmatrix}
  \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 & -G_{fc} \\
  G_{fc} &  \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2
\end{bmatrix}
\end{equation}

\subsection{Plant Dynamics}
\label{sec:org0a22a10}

@@

\subsection{Problems with Integral Force Feedback}
\label{sec:orgd432439}

@@

\section{Integral Force Feedback with High Pass Filters}
\label{sec:org2e1883a}
\subsection{Modification of the Control Low}
\label{sec:org218110f}
\begin{equation}
  \bm{K}_{F}(s) = \frac{1}{s} \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = \frac{1}{s + \omega_i}
\end{equation}

\subsection{Feedback Analysis}
\label{sec:org03090fc}

@@

\subsection{Optimal Cut-Off Frequency}
\label{sec:org6ba4e55}

@@

\section{Integral Force Feedback with Parallel Springs}
\label{sec:org90ec20f}
\subsection{Stiffness in Parallel with the Force Sensor}
\label{sec:org60d6640}

@@

\begin{equation}
\begin{bmatrix} f_u \\ f_v \end{bmatrix} =
\bm{G}_k
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}

\begin{equation}
\begin{bmatrix} f_u \\ f_v \end{bmatrix} =
\frac{1}{G_{kp}}
\begin{bmatrix}
   G_{kz} & -G_{kc} \\
   G_{kc} &  G_{kz}
\end{bmatrix}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}
With:
\begin{align}
  G_{kp} &= \left( \frac{s^2}{{\omega_0^\prime}^2} + 2\xi^\prime \frac{s}{{\omega_0^\prime}^2} + 1 - \frac{\Omega^2}{{\omega_0^\prime}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0^\prime}\frac{s}{\omega_0^\prime} \right)^2 \\
  G_{kz} &= \left( \frac{s^2}{{\omega_0^\prime}^2} + \frac{k_p}{k + k_p} - \frac{\Omega^2}{{\omega_0^\prime}^2} \right) \left( \frac{s^2}{{\omega_0^\prime}^2} + 2\xi^\prime \frac{s}{{\omega_0^\prime}^2} + 1 - \frac{\Omega^2}{{\omega_0^\prime}^2} \right) + \left( 2 \frac{\Omega}{\omega_0^\prime}\frac{s}{\omega_0^\prime} \right)^2 \\
  G_{kc} &= \left( 2 \xi^\prime \frac{s}{\omega_0^\prime} + \frac{k}{k + k_p} \right) \left( 2 \frac{\Omega}{\omega_0^\prime}\frac{s}{\omega_0^\prime} \right)
\end{align}

where:
\begin{itemize}
\item \(\omega_0^\prime = \frac{k + k_p}{m}\)
\item \(\xi^\prime = \frac{c}{2 \sqrt{(k + k_p) m}}\)
\end{itemize}

\subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
\label{sec:org3ec34fe}

\begin{equation}
  \frac{k_p}{k + k_p} - \frac{\Omega^2}{{\omega_0^\prime}^2} > 0
\end{equation}
Which is equivalent to
\begin{equation}
  k_p > m \Omega^2
\end{equation}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_iff_kp.pdf}
\caption{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kp.pdf}
\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\)}
\end{figure}

\subsection{Optimal Parallel Stiffness}
\label{sec:org9c47159}

@@

\section{Direct Velocity Feedback}
\label{sec:org5cb3076}
\subsection{Control Schematic}
\label{sec:orgaaa522f}

@@

\subsection{Equations}
\label{sec:orge0a4555}

\begin{equation}
\begin{bmatrix} v_u \\ v_v \end{bmatrix} =
\bm{G}_v
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}

\begin{equation}
\begin{bmatrix} v_u \\ v_v \end{bmatrix} =
\frac{s}{k} \frac{1}{G_{vp}}
\begin{bmatrix}
   G_{vz} & G_{vc} \\
  -G_{vc} & G_{vz}
\end{bmatrix}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}
With:
\begin{align}
  G_{vp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
  G_{vz} &= \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \\
  G_{vc} &= 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}
\end{align}

\subsection{Relative Direct Velocity Feedback}
\label{sec:org5401110}

@@

\section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
\label{sec:org4cbf163}
\subsection{Physical Comparison}
\label{sec:org5eba275}

\subsection{Attainable Damping}
\label{sec:org44635e0}

@@

\subsection{Transmissibility and Compliance}
\label{sec:org58e9594}

@@

\section{Conclusion}
\label{sec:org292b448}
\label{sec:conclusion}

\section*{Acknowledgment}
\label{sec:orgff7af07}
